---
title: "Rabies Database Pipeline Check Report"
author: "Michael Li, Jonathan Dushoff, Katie Hampson"
date: "`r format(Sys.time(), '%H:%M %d %B %Y')`"
output: 
  html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(shellpipes)
rpcall("SD_dogs.report.html report.rmd outdir/SD_dogs/stamp")

repName <- pipeStar()
outpath <- paste0("outdir/",repName,"/",repName)
csvpath <- function(x){paste0(outpath,".",x,".Rout.csv")}
```

This is the `r repName` report.

1. Run pipeline to see problematic cases
1. When cases are fixed on Wise Monkey:
	* Update the Dropbox
	* delete the file Animal_CT.csv
	* remake the report with "make `r repName`.report.html"

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

## ID Check

This check keeps a list of repeat IDs because dogs was repeatedly exposed.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
IDcheck <- read_csv(csvpath("IDCheck"))
repAnimals <- (IDcheck
  %>% select(code, ID)
  %>% distinct()
  %>% summarise(Count = n())
)
```

The file [IDcheck](`r csvpath("IDCheck")`) shows `r nrow(IDcheck)` records corresponding to `r repAnimals` unique animals that were apparently exposed repeatedly.


## Suspect Cases


```{r, echo=FALSE, message=FALSE, warning=FALSE}
SuspectCheck <- read_csv(csvpath("suspectCheck"))
```

Suspected cases showed signs of rabies (and therefore have a date of signs onset), and were exposed/bitten by another animal, bit another animal, or have at least one of the ten criteria indicative of suspect rabies (IF THEY WERE RECORDED AFTER DAT X - CAN YOU CHECK WHAT THIS IS!?).
<p style="color:red">MLi: The first case with suspect Yes/Todo with suspect criteria records is ID 224, on 2003-08-19, but records after 2010-01-01 looks more plausible. I am using 2010-01-01 as a soft cutoff.</p>

The file [suspectCheck](`r csvpath("suspectCheck") `) shows `r nrow(SuspectCheck)` records corresponding to `r SuspectCheck %>% select(ID) %>% distinct() %>% nrow()` unique animals with at least one of the following problems:

* __Suspect1__: `r SuspectCheck %>% filter(code == "Suspect1") %>% nrow()` records where _Suspect_ was recorded as __Yes__ and _Outcome_ as __Alive__.

* __Suspect2__: `r SuspectCheck %>% filter(code == "Suspect2") %>% nrow()` records where _Suspect_ was recorded as __Yes__ and _Outcome_ as __Todo__.

* __Suspect3__: `r SuspectCheck %>% filter(code == "Suspect3") %>% nrow()` records where _Symptoms started_ is __TRUE__ but no date or accuracy is recorded.

* __Suspect4__: `r SuspectCheck %>% filter(code == "Suspect4") %>% nrow()` records where _Symptoms started_ is __NA__ but _Suspect_ is __Yes__ or __To do__ and _Outcome_ is __Alive__.

    - __Suspect4__ are cases that were exposed/bitten by a suspected animal but did not show symptoms yet. We should be follow up on these cases first! 
    
* __Suspect5__: `r SuspectCheck %>% filter(code == "Suspect5") %>% nrow()` records where _Suspect_ was recorded as __Yes__ and 0/10 suspect criteria are TRUE (How well does the 10 suspect criteria match symptoms?)
** EDIT THIS TO ONLY APPLY TO DATA POST-DATE OF ELECTRONIC IMPLEMENTATION. I DON'T RECALL THIS - BUT YOU SHOULD BE ABLE TO WORK IT OUT!!! EITHER WAY THIS SHOULD BE A LATE STAGE CHECK!
<p style="color:red">MLi: I am checking all cases after 2010-01-01. It is not as clear as I thought working it out in the dataset.</p>

## Outcome Check

```{r, echo=FALSE, message=FALSE, warning=FALSE}
OutcomeCheck <- read_csv(csvpath("outcomeCheck"))
```

The file [outcomeCheck](`r csvpath("outcomeCheck") `) shows `r nrow(OutcomeCheck)` records corresponding to `r OutcomeCheck %>% select(ID) %>% distinct() %>% nrow()` unique animals where the outcome and action does not make sense and requires investigation.

* __OC1__: `r OutcomeCheck %>% filter(code == "OC1") %>% nrow()` records where _Outcome_ is __Alive__ or __Disappeared__ and _Action_ is not __NA__. For example, there are cases where _Outcome_ is __Alive__ and _Action_ is __Buried__!

* __OC2__: `r OutcomeCheck %>% filter(code == "OC2") %>% nrow()` records where _Outcome_ is __Alive__ nor __Disappeared__ and _Action_ is __NA__. 


## Wildlife Check

```{r, echo=FALSE, message=FALSE, warning=FALSE}
wildlifeCheck <- read_csv(csvpath("wildlifeCheck"))
```

Wildlife should not contain any information about itself (e.g. name, vaccination status) and owner. 

The file [wildlifeCheck](`r csvpath("wildlifeCheck")` shows `r nrow(wildlifeCheck)` records corresponding to `r wildlifeCheck %>% select(ID) %>% distinct() %>% nrow()` unique animals where the information does not match its wildlife status.

* __WL1__: `r wildlifeCheck %>% filter(code == "WL1") %>% nrow()` records where _Species_ is __wildlife__ with information about its name, owner, vaccination status or unknown if it is recorded as other species.

* __WL2__: `r wildlifeCheck %>% filter(code == "WL2") %>% nrow()` records where _Species_ is not __wildlife__ with a known owner but no information about owner's name or its vaccination status.

* __WL3__: `r wildlifeCheck %>% filter(code == "WL3") %>% nrow()` records where _Species_ is not __wildlife__ and without owner but information about its name, vaccination status and accuracy information about date bitten and symptom started.

## Infectious Period Check

Reported infectious periods should be <10 days. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
infCheck <- read_csv(csvpath("infCheck"))
```

The file [infCheck](`r csvpath("infCheck")`) shows `r nrow(infCheck)` records corresponding to `r infCheck %>% select(ID) %>% distinct() %>% nrow()` animals with infectious periods > 10 days.

## Incubation Period Check

MLi: TODO need a better naming rule for incubation

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#incubation <- read_csv(csvpath("incubation.check"))
incubation <- read_csv("outdir/SD_dogs/SD_dogs.incubation.check.csv")
```

The file [incubation](outdir/SD_dogs/SD_dogs.incubation.check.csv) shows `r nrow(incubation)` records corresponding to `r incubation %>% select(ID) %>% distinct() %>% nrow()` animals where incubation period is recorded as either < 3 days or the incubation period calculated from the date bitten and symptom date (dateInc) doesn't match the reported incubation period. 

* __inc1__: `r incubation %>% filter(code == "inc1") %>% nrow()` records where reported incubation period is less than 3 days. 

* __inc2__: `r incubation %>% filter(code == "inc2") %>% nrow()` records where reported incubation are suspected to have a unit mismatch. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(incubation 
      %>% filter(code == "inc2")
      %>% select(code, ID, dateInc, Incubation.period, Incubation.period.units)
)
```

